Is There a Correlation Between Preference and Perceptions of Inaction and Action in Decision-Making and Gender? An Analysis of Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes Study 2.

### 2024-02-15 outputs/paper/paper.qmd
paper update

## read in cleaned data 
data_gender = read_csv(
  file = "data_gender.csv",
  show_col_types = FALSE
)

data_male = read_csv(
  file = "data_male.csv",
  show_col_types = FALSE
)

data_female = read_csv(
  file = "data_female.csv",
  show_col_types = FALSE
)

@@

head (data_gender, 5) |>
  kable(
    col.names = c("Preference","Competence","Gender"),
  booktabs = TRUE
  )
```
Data used in this report was taken from the *Center for Open Science*, an open platform that aims to support collaborative research, from a project folder that contains all relevant replication data as uploaded by Fillion, Staunch, and Feldman [@giladpaper]. The specific data set was titled `inactionwetrust_study2.csv` and downloaded directly from the *Center for Open Science*. The data set was imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis.  Data was simulated with the functionalities of the `tibble` [@tibble] package. The raw data set was extracted and saved with the functionalities of the `readr` [@readr] package. Data cleaning was aided by the use of the `tidyverse` [@tidyverse], and `dplyr` [@dplyr] packages. To create tables and graphs for data visualization of the datasets, the `ggplot2` [@ggplot2] and `knitr` [@knitr] packages were used.

@@

### Preference of Action versus Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencemale
#| fig-cap: Distribution of Male Participants by Preference

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencefemale
#| fig-cap: Distribution of Female Participants by Preference

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferenceboth
#| fig-cap: Comparison of Gender Distribution by Preference

@@

### Perceived Competence of Action and Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencemale
#| fig-cap: Distribution of Male Participants by Competence Perception

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencefemale
#| fig-cap: Distribution of Female Participants by Competence Perception

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competenceboth
#| fig-cap: Comparison of Gender Distribution by Competence

>>>>

## read in cleaned data 
data_gender = read_csv(
  file = "~/Preference-and-Perception-of-Decision-Making/outputs/data/00-cleaned_study_2_data.csv",
  show_col_types = FALSE
)

data_male = read_csv(
  file = "~/Preference-and-Perception-of-Decision-Making/outputs/data/01-cleaned_study_2_men_data.csv",
  show_col_types = FALSE
)

data_female = read_csv(
  file = "~/Preference-and-Perception-of-Decision-Making/outputs/data/02-cleaned_study_2_women_data.csv",
  show_col_types = FALSE
)

@@

head (data_gender, 5) |>
  kable(
    col.names = c("Preference","Competence","Gender"),
  booktabs = TRUE
  )
```
Data used in this report was taken from the *Center for Open Science*, an open platform that aims to support collaborative research, from a project folder that contains all relevant replication data as uploaded by Fillion, Staunch, and Feldman [@giladpaper]. The specific data set was titled `inactionwetrust_study2.csv` and downloaded directly from the *Center for Open Science*. The data set was imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis.  Data was simulated with the functionalities of the `tibble` [@tibble] package. The raw data set was extracted and saved with the functionalities of the `readr` [@readr] package. Data cleaning was aided by the use of the `tidyverse` [@tidyverse], `photobiology` [@photobiology], and `dplyr` [@dplyr] packages. To create tables and graphs for data visualization of the data sets, the `ggplot2` [@ggplot2] and `knitr` [@knitr] packages were used.

@@

### Preference of Action versus Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses Across Men

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferencefemale
#| fig-cap: Frequency of Decision-Making Approach Preference Responses Across Women

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-preferenceboth
#| fig-cap: Comparison of Decision-Making Approach Preference Response Frequencies by Gender

@@

### Perceived Competence of Action and Inaction Agents by Gender
```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencemale
#| fig-cap: Frequency of Competence Perception Responses Across Men

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competencefemale
#| fig-cap: Frequency of Competence Perception Responses Across Women

@@

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: fig-competenceboth
#| fig-cap: Comparison of Percieved Competence Participant Response Frequencies by Gender
